---
title: "Solutions 2"
author: "Sanjeev Gadre"
date: "September 12, 2018"
output: md_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
library(stringr)
library(tidyr)
data("College")
data("mtcars")
```

These are solutions to the exercises found at http://r-tutorials.com/r-exercises-61-70-string-manipulation-gsub-regex-regular-expressions/

###2.1
```{r 2-1}
college.names=row.names(College)
texas.colleges=str_match(college.names, "Texas")
summary(texas.colleges)
texas.colleges.index=which(texas.colleges[,1]=="Texas")
texas.colleges.index
texas.college.details = College[texas.colleges.index,]
head(texas.college.details)
```

###2.2
```{r 2-2}
college.names = str_split(college.names,"\\s", n=Inf)
head(college.names)

college.names = str_to_lower(college.names)
head(college.names)

college.names = casefold(college.names, upper=TRUE)
head(college.names)
```

###2.3
```{r 2-3}
College %>% rownames() %>% str_which("University")

College %>% rownames() %>% str_which("University") %>% length()
College %>% rownames() %>% str_which("College") %>% length()
```

There is an error in the solution key provided on the page for counting the number of "College". It uses str_count() and then sum() to find out the number of entries with "College" in them. However, "Arkansas College (Lyon College)" will return a value of 2 as "College" appears twice and incorrectly increases the number of entries with "College" in them to 406. My solution of str_which() followed by length() avoids this "double counting". This error is present also for the code used to count the number of "University".

###2.4
```{r 2-4}
"get" %>% str_pad(10, side="both", pad="0")

paddedstring = "Oslo" %>% str_pad(10, side="left", pad=" ")
paddedstring

paddedstring %>% str_trim(side="left")

paddedstring %>% str_trunc(7, side="left")
```


###2.8
```{r 2-8}
mtcars.names = rownames(mtcars)
head(mtcars.names)

mtcars.names %>% str_replace_all("\\d+", "") %>% str_replace_all("[:punct:]", "") %>% str_replace_all("\\s", "") %>% str_replace_all("[:upper:]", "") %>% str_replace_all("[:lower:]", "")
```

###2.9
```{r 2-9}
mtcars.names %>% str_replace_all("Merc(?=\\b)", "Mercedes")
```

###2.10
```{r 2-10}
mystring = "Gabriel-Henry.Tedd.-John (Yorkshire)"

mystring %>% str_replace_all("\\.", " ")

mystring %>% str_replace_all("\\s*\\([^\\)]*\\)", "")
```

