---
title: "Solutions 6"
author: "Sanjeev Gadre"
date: "September 27, 2018"
output: md_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(dplyr)
library(babynames)
```

These are solutions to the exercises found at: https://www.r-exercises.com/2017/07/14/hacking-strings-with-stringr/. I have used the stringr library to solve these exercises

###6.1
```{r 6-1}
x = "I AM SAM. I AM SAM. SAM I AM"
y = "THAT SAM-I-AM! THAT SAM-I-AM! I DO NOT LIKE THAT SAM-I-AM!"
z = "DO WOULD YOU LIKE GREEN EGGS AND HAM?"

answer.6.1 = str_c(x,y,z, sep=" ")
answer.6.1
```

###6.2
```{r 6-2}
dat = c(x,y,z,NA)

answer.6.2.a = paste(dat, sep=" ", collapse=" ")
answer.6.2.a

answer.6.2.b = str_c(dat, sep=" ", collapse=" ")
answer.6.2.b
```

The paste() simply treats NA element of the vector as another string and concatenates to the other strings in the vector. str_c() on the other hand gives an NA output if one of the elements is NA. To convert the NA to a literal NA we use str_replace_na() - `str_c(str_replace_na(dat), sep=" ", collapse=" ")`

###6.3
```{r 6-3}
data("babynames")
str_length(head(babynames$name)) #The vector length is very large and hence restricting it using the head()
```


###6.4
```{r 6-4}
dat = "Sanjeev Gadre"
str_sub(dat, -1L)
str_sub(dat, -5L)
```

###6.5
```{r 6-5}
data("mtcars")
rownames(mtcars) %>% str_subset("Merc")
```

###6.6
```{r 6-6}
rownames(mtcars) %>% str_count("e") %>% sum()
```

###6.7
```{r 6-7}
j <- "The_quick_brown_fox_jumps_over_the_lazy_dog"
str_split(j, pattern="_", n=Inf, simplify=FALSE)
```

###6.8
```{r 6-8}
str_split(j, pattern="_", n=2, simplify=FALSE)
```

###5.9
```{r 5-9}
str_replace(j, "_", "-")
str_replace_all(j, "_", "-")
```

###5.10
```{r 5-10}
na_string_vec = c("The_quick_brown_fox_jumps_over_the_lazy_dog",NA)
str_replace_na(na_string_vec, "NA")

```

